---
title: "HFR 2020.09"
output: html_document
---

```{r install and/or load R packages}
library(tidyverse)
devtools::install_github("USAID-OHA-SI/Wavelength")
library(Wavelength)
library(stringr)
library(purrr)
```

```{r list functions in package}
ls("package:Wavelength")
```

```{r setting Working directory}
getwd()
setwd("C:/Users/dolee/Desktop/HFR")
pdfolder <- "C:/Users/dolee/Desktop/HFR/2020.09"
output_folder <- "C:/Users/dolee/Desktop/HFR/2020.08/Output"
```

```{r API pull (optional)}
#packages to install: keyringr, curl, httr, jasonlite
#MER results & targets
#org heirarchy
#mechanism and partner information
```

```{r reading in HFR file (optional)}
path <- "./"
df <- hfr_read(path)
```

```{r reading in org_levels, orgs, ims, valid_dates}
valid_dates <- Wavelength::hfr_identify_pds(fy=2020)
org_levels <- read_csv("./HFR_FY20_GLOBAL_orglevels.csv")
orgs <- read_csv("./HFR_FY20_GLOBAL_orghierarchy_20200611.csv")
ims <- read_csv("./HFR_FY20_GLOBAL_mechanisms_20200611.csv")
iso_map
```

```{r inspect org_levels, orgs, ims, valid_dates (optional)}
ims %>%
  glimpse() %>%
  filter(operatingunit=="South Africa") %>%
  distinct(fundingagency, mech_name, mech_code) %>%
  print(n=Inf)

orgs %>%
  filter(operatingunit=="Zambia") %>%
  filter(str_detect(orgunit, "Kamu")) %>%
  print(n=Inf)
```

2020.09

Asia/India
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*INDIA", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

Asia/India prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*_XAR", source=T)
hfr_data %>% 
  distinct(psnu) %>%
  distinct(source) %>%
  print(n=Inf)
```

Burundi
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*Burundi", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

Burundi prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*_BDI", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

Nigeria
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*RP09", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

Nigeria prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*NGA", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

Zimbabwe
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*Zimbabwe", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

Zimbabwe prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*ZWE", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

Ukraine
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*Ukraine", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

Ukraine prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*UKR", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

Botswana
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*Botswana", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

Botswana prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*BWA", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

Vietnam
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*Vietnam", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

Vietnam prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*VNM", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

KAZ 100176
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*KZ_", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

KAZ prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*XAR", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

KGZ 10076
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*KZ", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

KGZ prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*XAR", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

TJK 
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*TJ", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

TJK prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*XAR", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

NPL 9
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*NEPAL", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

NPL 9 prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*NPL", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

NPL 8 prep for extra
```{r}
hfr_data <- hfr_read_all(output_folder, pattern = "*NPL", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

LAO 
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*Laos", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

LAO prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*XAR_100194", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

IND
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*INDIA", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

IND prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*XAR", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

UGA
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*Uganda", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

UGA prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*UGA", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

IDN
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*Indonesia", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

IDN prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*XAR", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

THA
```{r Validation check}
#pd9
files <- list.files(path="./2020.09", pattern = "*Thailand", full.names=TRUE)
files
purrr::walk(files, hfr_process_template)
purrr::walk(files, hfr_process_template, round_hfrdate=TRUE, hfr_pd_sel=9, folderpath_output=output_folder)
```

THA prep for extra
```{r Read in processed file for extra validaion check}
?hfr_read_all
hfr_data <- hfr_read_all(output_folder, pattern = "*XAR", source=T)
hfr_data %>% 
  distinct(source) %>%
  print(n=Inf)
```

Check for invalid OUs
```{r Check for invalid operating units}
hfr_data %>%
        is_ou_valid(df_orgs = orgs) %>%
        filter(valid_ou == F) %>%
        distinct(source, operatingunit, valid_ou) %>%
        arrange(source)

# Use mechanism code to update operating units
    hfr_data <- hfr_data %>%
        update_operatingunits(levels=org_levels, orgs=orgs, ims=ims)
    
# Check if there are still any invalid operating units (for invalid mech_code)
    hfr_data %>%
        is_ou_valid(df_orgs = orgs) %>%
        filter(valid_ou == FALSE) %>%
        View()
# Use iso3 code (second attempt)
    hfr_data <- hfr_data %>%
        update_operatingunits(levels=org_levels, orgs=orgs)
  
# Check again for invalid operating units 
    hfr_data %>%
        is_ou_valid(df_orgs = orgs) %>%
        filter(valid_ou == FALSE) %>%
        View()
```

Run full validation
```{r Run full validation on the data (with all the operating units errors fixed)}
#validate hfr data from processed files and return errors
errors <- validate_hfr_data(hfr_data, org_levels, orgs, ims, valid_dates)
  
#Explore the errors
errors %>% 
  glimpse() %>%
  distinct(source)

#Explore the errors by pd
errors_df <- errors %>%
  filter(grepl('2020.01_ZAF', source))

errors_df %>%
  distinct(source)
```

Fix error with UID lookup
```{r Fix errors...}
?hfr_orgunit_search

hfr_orgunit_search(orgs, 
                   orgunit_name = "Mercy Hospital",
                   ou="Nigeria") %>% print(n=Inf)
```

```{r Confirm all validations by marking valid processed files as validated files}
confirm_validations(hfr_data = hfr_data, 
                    hfr_errors = errors, 
                    dir_files = output_folder)
?confirm_validations
```

Inspect values in processed files
```{r}
outputs <- list.files(path=output_folder, pattern="*CMR*",full.names=T)
df <- sapply(outputs, read_csv, simplify=FALSE) %>% bind_rows(.id="id")
hfr_data %>%
  glimpse() %>%
  dplyr::group_by(operatingunit, date, indicator, agecoarse, sex) %>% 
  dplyr::summarize(val = sum(val, na.rm = TRUE)) %>% print(n=Inf)
```

iso_map %>% print(n=Inf)

